---
title: "LGH 6th floor seasonality of AD"
author: "Hans Aisake"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#move to a main file later I guess
#set library and working directories
libPath <-"H:/Hans/R Libraries"
.libPaths(libPath) #set the library path

#set WD
wd <- "//vch.ca/departments/VCHDecisionSupport/Coastal_Richmond_SI/2019-08-28_LGH_6th-floor-transfers-seasonality"
setwd(wd)

library(odbc) #for database connections
library(Rmarkdown)
library(tidyverse)
library(prophet)
library(here)
library(lubridate)
library(readxl)

# dsn_name <- "AISAKE-DENODO" #my OBDC denodo connection name
# channel <- DBI::dbConnect(odbc::odbc(), dsn = dsn_name)
# data <- dplyr::tbl(channel, dbplyr::in_schema("publish","activity_loc_room"))

#load source files

```

## R Markdown

<placeholder>
```{r cars}

data %>%
    dplyr::filter(  facility_short_name ='LGH',  
              beg_effective_date_id >= 20190601,
              beg_effective_date_id <= 20190630,
              nursing_unit_short_desc %in% 'LGH 6W') %>%
  
  dplyr::select(beg_effective_date_id,
              nursing_unit_short_desc,
              facility_short_name) %>%  # show_query()
  
#+ data 
# read in data -------
df1.activity <- 
  read_excel(here::here("Input", 
                      file="transfersDataLGH6Floor.xlsx"
                      , sheet = "data")) 

# %>% 
# 
#   mutate(censusdate = mdy(censusdate), 
#          NursingUnitDesc = as.factor(NursingUnitDesc))


df2.6e <- 
  df1.census_daily %>% 
  filter(NursingUnitDesc == "LGH 6E") %>% 
  select(censusdate, 
         Census) %>% 
  rename(ds = censusdate, 
         y = Census)


df3.6w <- 
  df1.census_daily %>% 
  filter(NursingUnitDesc == "LGH 6W") %>% 
  select(censusdate, 
         Census) %>% 
  rename(ds = censusdate, 
         y = Census)

df4.sco <- 
  df1.census_daily %>% 
  filter(NursingUnitDesc == "LGH SCO") %>% 
  select(censusdate, 
         Census) %>% 
  rename(ds = censusdate, 
         y = Census)


#+ models ----

#' ## Fit model for LGH 6E 
m1 <- prophet(df2.6e)

future <- make_future_dataframe(m1, 
                                periods = 10,
                                freq = "day")  

fcast <- predict(m1, future)

# plots 
plot(m1, fcast)
prophet_plot_components(m1, fcast)





#' ## Fit model for LGH 6W
m2 <- prophet(df3.6w)

future <- make_future_dataframe(m2, 
                                periods = 10,
                                freq = "day")  

fcast <- predict(m2, future)

# plots 
plot(m2, fcast)
prophet_plot_components(m2, fcast)




#' ## Fit model for LGH SCO
m3 <- prophet(df4.sco)

future <- make_future_dataframe(m3, 
                                periods = 10,
                                freq = "day")  

fcast <- predict(m3, future)

# plots 
plot(m3, fcast)
prophet_plot_components(m3, fcast)
