---
title: "LGH 6th floor seasonality of AD"
author: "Hans Aisake"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#move to a main file later I guess
#set library and working directories
libPath <-"H:/Hans/R Libraries"
.libPaths(libPath) #set the library path

#set WD
wd <- "//vch.ca/departments/VCHDecisionSupport/Coastal_Richmond_SI/2019-08-28_LGH_6th-floor-transfers-seasonality"
setwd(wd)

library(odbc) #for database connections
library(Rmarkdown)
library(dplyr)
library(tidyverse)
library(prophet)
library(lubridate)
library(readxl)
library(tidyverse)
library(here)
library(DBI)
library(ggbeeswarm)
library(DT)
library(broom)
library(caret)
library(kableExtra)
library(scales)

knitr::opts_chunk$set(dev = "png", cache = TRUE)

# dsn_name <- "AISAKE-DENODO" #my OBDC denodo connection name
# channel <- DBI::dbConnect(odbc::odbc(), dsn = dsn_name)
# data <- dplyr::tbl(channel, dbplyr::in_schema("publish","activity_loc_room"))

#load source files
source("./LGH-6-Floor/processData.R")

```

#' ## Data

````{r data, include=TRUE}


````{r loadData, echo=FALSE}
 #read in data from Excel extracted via DBVisualizer
  df1.activity <- read_excel(path="./Input/transfersDataLGH6Floor.xlsx", sheet = "data")

  df2.entries <- processData(df1.activity,"begin") #turn into the required data type
  df3.departures <- processData(df1.activity,"end") #turn into the required data type
````

#' ## Exploratory Plots

````{r exploratory plots}

df2.entries %>% 
  ggplot(aes(x = year, 
             y = entries)) + 
  geom_boxplot() + 
  facet_wrap(~dow) + 
  theme_light() +
  theme(panel.grid.minor = element_line(colour = "grey95"), 
        panel.grid.major = element_line(colour = "grey95"),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(title ="Histogram of entries on the LGH 6th floor by DOW  2018-05-01 to 2019-09-11")

df2.entries %>% 
  ggplot(aes(x = tod, 
             y = entries)) + 
  geom_boxplot() + 
  theme_light() +
  theme(panel.grid.minor = element_line(colour = "grey95"), 
        panel.grid.major = element_line(colour = "grey95"),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(title ="Histogram of entries on the LGH 6th floor by TOD 2018-05-01 to 2019-09-11")


df2.entries %>% 
  ggplot(aes(x = entries)) + 
  geom_bar() + 
  facet_wrap(~year) + 
  theme_light() +
  theme(panel.grid.minor = element_line(colour = "grey95"), 
        panel.grid.major = element_line(colour = "grey95"),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1))


````

```{r summary_and_load}
# 
# fit2019 <- 
#   df2.entries %>% 
#   filter(year == 2019) %>% 
#   pull(entries) %>% 
#   fitdistrplus::fitdist("norm")
#   
# # str(fit2019)
# summary(fit2019)

#not normally distributed there are definitely explanatories???
# plot(fit2019)


  x <- df2.entries %>% group_by(tod) %>% summarize(avg_entries = mean(entries), sd_entries = sd(entries), numTransfers = sum(entries))
  y <- df3.departures %>% group_by(tod) %>% summarize(avg_departures = mean(departures), sd_departures = sd(departures), numTransfers = sum(departures))

#+ models entries----  

  #split the data into a training and test set
  df2.entries$id <- 1:nrow(df2.entries)
  train <- df2.entries %>% dplyr::sample_frac(.75)
  test  <- dplyr::anti_join(df2.entries, train, by = 'id')

  ###########
  # Model 1
  ###########
  m1 = lm(data=train, entries ~year+ month+ tod + dow)
  summary(m1)  #rsquared 0.4195  , RMSE 0.8006
  predictions_m1 <- data.frame(predicted = predict(m1,newdata = test), test)
  m1.test_rmse <- sqrt(mean((predictions_m1$predicted - predictions_m1$entries)^2, na.rm = TRUE)) #0.7834701
  #model is not over fitting
  
  ###########
  # Model 2
  ###########  
  m2 = lm(data=train, entries ~year+ month+ tod + dow + tod:dow)
  summary(m2)  #rsquared 0.4549  , RMSE 0.7758
  predictions_m2 <- data.frame(predicted = predict(m2,newdata = test), test)
  m2.test_rmse <- sqrt(mean((predictions_m2$predicted - predictions_m2$entries)^2, na.rm = TRUE)) ??0.766701
  #model is not over fitting

  ##########
  # Model 1 seams to be simpler and just as good as Model 2. Going with model 1. Apply to all data
  #########
  m1 = lm(data=df2.entries, entries ~year+ month+ tod + dow)
  temp <- summary(m1)  #rsquared 0.4207  , RMSE 0.7958
  
  #generate the point with line charts
  df.coeff <- as.data.frame( temp$coefficients )
  df.coeff$lower <- df.coeff$Estimate-2*df.coeff$`Std. Error`
  df.coeff$upper <- df.coeff$Estimate+2*df.coeff$`Std. Error`
  

#+ models departures----  
  
  ###### Departures
  #split the data into a training and test set
  df3.departures$id <- 1:nrow(df3.departures)
  train <- df3.departures %>% dplyr::sample_frac(.75)
  test  <- dplyr::anti_join(df3.departures, train, by = 'id')

  ###########
  # Model 1
  ###########
  m1 = lm(data=train, departures ~year+ month+ tod + dow)
  summary(m1)  #rsquared 0.4973  , RMSE 0.8586
  predictions_m1 <- data.frame(predicted = predict(m1,newdata = test), test)
  m1.test_rmse <- sqrt(mean((predictions_m1$predicted - predictions_m1$departures)^2, na.rm = TRUE)) #0.8680379
  #model is not over fitting???
  
  ###########
  # Model 2
  ###########  
  m2 = lm(data=train, departures ~year+ month+ tod + dow + tod:dow)
  summary(m2)  #rsquared 0.5229  , RMSE 0.8364
  predictions_m2 <- data.frame(predicted = predict(m2,newdata = test), test)
  m2.test_rmse <- sqrt(mean((predictions_m2$predicted - predictions_m2$departures)^2, na.rm = TRUE)) #0.8484416
  #model is not over fitting

  ##########
  # Model 1 seams to be simpler and just as good as Model 2. Going with model 1. Apply to all data
  #########
  m1 = lm(data=df3.departures, departures ~year+ month+ tod + dow)
  temp <- summary(m1)  #rsquared 0.4207  , RMSE 0.7958
  
  
  
